From Freebase to Wikidata: The Great Migration

### 2015-10-15 paper.tex
Added cats and other meta

% a~category with the (minimum) three required fields
\category{H.4}{\todo{Hierarchy}}{Miscellaneous}

\terms{\todo{Terms}}

\keywords{\todo{Keywords}}

@@

Freebase is an open source and
collaborative knowledge base created in 2007 by Metaweb and 
acquired in 2010 by Google~\cite{freebase}.
It was used as the open core of the Google Knowledge Graph,
and also has many use cases outside of Google.

Due to the success of Wikidata,
it was decided to close Freebase and support the migration of its content to Wikidata.
Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
Each Freebase topic has a~stable identifier called \emph{``mid''} (for Metaweb ID),
one or more types, and uses properties from these types in order to provide facts.
For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
and the type \texttt{/government/us\_president} (among others) that allows the entity to have
a fact with the property \texttt{/government/us\_president/presidency\_number}
and the literal integer ``44'' as the value.

@@

To represent complex values like geographic coordinates or to annotate relations,
for example, in order to add start and end dates for a~position held,
Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig:cvt-obama}).
They behave like topics, \emph{e.g.}, have a~mid and can have types,
but do not have the \texttt{/common/topic} type.

>>>>

\category{H.3.5}{Information Storage and Retrieval}{Online Information Systems}
\category{H.5.3}{Information Interfaces}{Group and Organization Interfaces?Web-based interactions}
\category{I.2.4}{Artifical Intelligence}{Knowledge Representation}
\category{K.4.3}{Computers and Society}{Organizational Impacts Computer-supported collaborative work}

\terms{Human Factors, Documentation}

\keywords{AIW: AI for Web-Based Collaboration and Cooperation, AIW: Crowdsourcing Techniques and Methodologies, KRR: Knowledge Acquisition}

@@

Freebase is an open and
collaborative knowledge base created in 2007 by Metaweb and 
acquired in 2010 by Google~\cite{freebase}.
It was used as the open core of the Google Knowledge Graph,
and has found many use cases outside of Google.
Due to the success of Wikidata,
Google announced in 2014 to close Freebase and offer most of its content to the
Wikidata community~\cite{freebase-end}.

Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
Each Freebase topic has a~stable identifier called \emph{``mid''} (for Metaweb ID),
one or more types, and uses properties from these types in order to provide facts.
For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
and the type \texttt{/government/us\_president} (among others) that allows the entity to have
a fact with the property \texttt{/government/us\_president/presidency\_number}
and the literal integer ``44'' as the value.

@@

Freebase uses Compound Value Types (CVTs, see \autoref{fig:cvt-obama}) to represent
n-ary relations with $n>2$, e.g. values like geographic coordinates,
political positions held with a start and end date, or actors playing a specific character in a movie.
CVT values are much like topics, \emph{i.e.} they have a~mid and can have types
(usually only the compound value type).
